---
title: "Resampling"
author: "Christopher Brown"
date: "October 5, 2015"
output: html_document
---


```{r}
set.seed(314159)
```


Use the `baseball` data set from the `plyr` package for the following problem.

A very simple model to predict the number of at-bats/game **each** player has per game is given by: 
 
     abpg = sum(ab)/sum(g)  # 3.10
     

- Show that this is a bad:

```{r}
library(plyr)
data(baseball)


baseball$pred_abpg <- with(baseball, sum(ab)/sum(g))
baseball$error <- (baseball$ab/baseball$g)-baseball$pred_abpg
sqrt((sum(baseball$error^2, na.rm=T)) / length(baseball$error))
```



- Create a better model using only number of games as a predictor

```{r}
fit <- lm(ab ~ g, data=baseball)
summary(fit)
```


- Calculate the "Apparent" *RMSE* of this model.    

```{r}
rmse <- function(y,yhat)
  (y-yhat)^2 %>% mean %>% sqrt
rmse(fit$fitted.values, baseball$ab)
```


Using only Recreate the model, providing a new estimate for `ab/g` and the RMSE, using:
- 5-Fold CV
- Bootstrap

```{r}
bs <- sample(nrow(baseball), replace=T)


```

