---
title: "Boston Housing"
author: 'Jennifer Borkowsky (email: jb3131@gmail.com)'
date: "Wednesday, September 23, 2015"
output: html_document
---

The *mlbench* package contains the data set `BostonHousing`. 

Create a linear regression model that predicts the medium home value of the census tract as a function of the relevant predictors. Please refer to the process diagram from class. Don't forget to examine the response and predictors variable using graphical and other means.  Show your work.

This is a `rmarkdown` Document. You can use `rmarkdown` to produce a Word Doc
file, a presentation, html file, etc. Please just submit the code.


*(a) Load libraries, get data*
```{r, warning=F}
library(reshape2)
library(mlbench)
library(magrittr)
library(ggplot2)
data(BostonHousing)
```

*(b) define root mean squared error function to use in model evaluation*
```{r}
rmse <- function(y,yhat)
  (y-yhat)^2 %>% mean %>% sqrt
```

*(c) Data exploration*

*Plot response variable - median value of homes*
```{r, fig.width=4, fig.height=3, warning=F}
qplot(BostonHousing$medv)
```

*Median value of homes is slightly skewed to right; possible violation of linear regression assumptions*

*Examine correlation coefficients for pairs of numeric variables in BostonHousing data set*
```{r}
cor(BostonHousing[sapply(BostonHousing, is.numeric)]) 

#Propery tax and index of accessibility to radial highways are highly correlated, check plot
ggplot(BostonHousing, aes(x=tax, y=rad)) +
  geom_point() +
  geom_smooth(method=lm)
#Looks as though an outlier is causing correlation

#Other highly correlated variables (|r|>.7):
pairs(~nox+indus+tax+age+dis, data=BostonHousing)
#correlation between nitric oxide concentration and distance to employment centers could be a problem
```

*(d) Model fitting*
```{r}
# fit model with all predictors
fit <- lm(medv~ . , data=BostonHousing)
summary(fit)
# evaluate model using root mean squared error as a measure of fit
rmse(fit$fitted.values, BostonHousing$medv)
```

```{r}
# remove non-significant predictor age
fit2 <- lm(medv~ . -age , data=BostonHousing)
summary(fit2)
# evaluate model using root mean squared error as a measure
rmse(fit2$fitted.values, BostonHousing$medv)
```

```{r}
# remove non-significant predictor proportion of non-retail business acres
fit3 <- lm(medv~ . -age -indus , data=BostonHousing)
summary(fit3)
# evaluate model using root mean squared error as a measure
rmse(fit3$fitted.values, BostonHousing$medv)
```

*All remaining predictors are significant.  This model has the highest RMSE, but it is only a very slight increase, and due to a more parsimonious model*

*Check predicted values against actual values of median home value*
```{r, fig.width=6, fig.height=5}
df <- data.frame(BostonHousing$medv, fit3$fitted.values)
ggplot(melt(df), aes(value, fill = variable)) + geom_histogram(position = "dodge")
```

*The model seems to give a good prediction of median home values given the set of predictors.*
