---
title: "week4 assignments"
author: "Christopher Brown"
date: "September 30, 2015"
output: html_document
---

# Readings

In **Applied Predictive Modeling** (APM), Read:
- Chapter 4 - Overfitting and Model Tuning
- Chapter 5 - Regression Models
- Chapter 6 , esp. 6.2 - Linear Regression
- Chapter 12.2 - Logistic Regression 



# Problem Set 

DUE: *In Class Monday October 12th*

The assigments are designed to be completed using [RMarkdown](http://rmarkdown.rstudio.com/). 

> R Markdown is an authoring format that enables easy creation of dynamic 
> documents, presentations, and reports from R. It combines the core syntax of
> markdown (an easy-to-write plain text format) with embedded R code chunks that
> are run so their output can be included in the final document. R Markdown
> documents are fully reproducible (they can be automatically regenerated 
> whenever underlying R code or data changes).


For questions requiring: 

- textual answers: record your answer in plain text
- code: place the code in the RMarkdown code fence. 

Show all code used to arrive at the answers.



## ***APM*** 6.2 (a)-(d)

```{r}
library(AppliedPredictiveModeling)
library(caret)
library(pls)
data(permeability)
```

(a) No response required.

(b)   

```{r}
fp <- fingerprints[, -nearZeroVar(fingerprints)]
ncol(fp)
```

389 predictors are left for modeling

(c)
```{r}
# add response data to predictors
fp <- data.frame(fp)
fp$perm <-permeability

## 75% of the sample size
sampsize <- floor(0.75 * nrow(filtered))

## set the seed to make partition reproductible
set.seed(123)
train_ind <- sample(seq_len(nrow(filtered)), size = sampsize)

## split data into training and test data sets
train <- fp[train_ind, ]
test <- fp[-train_ind, ]
```

(d) 
```{r}
plsFit <- plsr(perm ~ ., data=train, validation="LOO")
summary(plsFit)
plot(RMSEP(plsFit))
predict(plsFit, test)
```


## ***APM*** 6.3 


